---
title: "2012 incubation CO2 flux and 14C plots"
author: "Lydia Vaughn"
date: "February 6, 2018"
output: html_document
---

Data: radiocarbon_incubation_Barrow_2012.csv includes CO2 flux rates and radiocarbon values from incubated soils.  File and data description can be accessed at http://dx.doi.org/10.5440/1364062.  naming.csv links conflicting identifiers used for soil samples.  soil_mass.csv lists dry soil masses for each incubated sample.  naming.csv and soil_mass.csv can be found at https://github.com/lydiajsvaughn/Radiocarbon_inc_2012/tree/master/data

```{r global_options, include=FALSE}
knitr::opts_chunk$set(message=FALSE)
```

```{r}
inc <- read.csv('data/radiocarbon_incubation_Barrow_2012.csv', stringsAsFactors=F)
naming <- read.csv('data/naming.csv', header=T, sep=',', stringsAsFactors=F)
mass <- read.csv('data/soil_mass.csv', header=T, sep=',', stringsAsFactors=F)
```

```{r}
library(lubridate)
library(gridExtra)
library(tidyverse)
```

Make a column identifying each layer as shallow, middle, or deep
```{r}
inc <- inc %>% group_by(plot_ID) %>% mutate(depth_increment = ifelse(layer_top==min(layer_top), "Shallow", ifelse(layer_bot==max(layer_bot), "Deep", "Middle"))) 

inc$depth_increment <- factor(inc$depth_increment, levels=c("Shallow", "Middle", "Deep"), ordered=T)

```

Calculate CO2 flux in mg C per day and format dates
```{r}
inc <- inc %>% left_join(mass) %>% mutate(CO2flux_total = CO2_production * mass_drysoil_g, sample_date = as.Date(sample_date, '%m/%d/%y'))

inc$sample_type <- ifelse(is.na(inc$sample_type), "CO2", inc$sample_type)
```

Calculate soil carbon (g) at the beginning and end of each incubation period by accounting for losses as CO2 during each  period.  Calculate the mean soil carbon (g) during each incubation period
```{r}
#Period 1 = 13 day incubation plus 1 day post-incubation at 5 degrees 
#Period 2 = 5 day preincubation and 16 day incubation at 10 degrees
#Period 3 = 4 day preincubation and 21 day incubation at 5 degrees

wide <- inc %>% filter(sample_type == "CO2") %>% select(-starts_with("oc")) %>% left_join(inc %>% filter(sample_type == "soil") %>% select("plot_ID", "layer_top", "layer_bot", "oc")) 

wide <- wide %>% group_by(sample_name) %>% summarize(oc = mean(oc)) %>% full_join(wide %>% select(-starts_with("oc"))) %>% distinct()

#Period 3 with starting and ending soil C masses
per3 <- wide %>% filter(sample_date == "2012-10-22") %>% mutate(soilC_end = oc / 100 * mass_drysoil_g, soilC_start = oc / 100 * mass_drysoil_g + CO2flux_total * 21 / 1000, per2_end = soilC_start + CO2flux_total * 3 / 1000) 

#Period 2 with starting and ending soil C masses
per2 <- wide %>% filter(sample_date == "2012-09-27") %>% left_join(per3 %>% select("plot_ID", "layer_top", "layer_bot", "per2_end")) %>% rename("soilC_end" = "per2_end") %>% mutate(soilC_start = soilC_end + CO2flux_total * 16 / 1000, preinc_end = soilC_start + CO2flux_total * 5 / 1000) 

#Period 1 with starting and ending soil C masses
per1 <- wide %>% filter(sample_date == "2012-09-04") %>% left_join(per2 %>% select("plot_ID", "layer_top", "layer_bot", "preinc_end")) %>% mutate(soilC_end = preinc_end + CO2flux_total * 1 / 1000, soilC_start = soilC_end + CO2flux_total * 13 / 1000) 
wide_carbon <- per1 %>% select(-starts_with("preinc")) %>% full_join(per2 %>% select(-starts_with("preinc"))) %>% full_join(per3 %>% select(-starts_with("per2_end"))) %>% mutate(soilC_mean = (soilC_end + soilC_start) / 2)
```

For each incubation period, calculate CO2 flux in mg C respired per day per g soil C and g C respired per day per g soil C (i.e., k)
```{r}
wide_carbon <- wide_carbon %>% mutate(CO2flux_mg_g_d = CO2flux_total / soilC_mean, k = CO2flux_total / 1000 / soilC_mean)
```

For each incubation period, calculate the mean, sd, and se CO2 flux in mgC per g soil C per day
```{r}
fluxmean <- wide_carbon %>% group_by(sample_date) %>% summarize(meanflux = mean(CO2flux_mg_g_d), sdflux = sd(CO2flux_mg_g_d), nflux = length(CO2flux_mg_g_d)) %>% mutate(seflux = sdflux / nflux^0.5)
```

Themes for plots
```{r}
plottheme <- theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  theme(axis.text.y = element_text(color="black", size=8)) +
  theme(axis.text.x = element_text(color="black", size=10, angle=90, vjust=0.5)) +
  theme(axis.title.y = element_text(color="black", size=10)) +
  theme(axis.title.x = element_blank()) +
  theme(legend.text = element_text(size=8)) +
  theme(legend.title = element_text(size=10)) 

plottheme2 <- plottheme + theme(axis.text.x = element_text(size=10, angle = 0))

plottheme3 <- plottheme + 
  theme(axis.title.x = element_text(color="black", size=10)) +
  theme(axis.text.x = element_text(color="black", size=8, angle = 0)) 

plottheme4 <- theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  theme(axis.text.y = element_text(color="black", size=8)) +
  theme(axis.title.y = element_text(color="black", size=9)) +
  theme(axis.text.x = element_text(color="black", size=9, margin = margin(t = 10))) +
  theme(axis.title.x = element_blank())  +
  theme(plot.title = element_text(size = 10, face = "bold"))
  #theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))

facettheme <- theme(strip.text = element_text(size=10)) +
  theme(strip.background = element_rect(colour="white", fill="white")) +
  theme(panel.spacing = unit(.5, "lines")) 
```

Plot the mean flux per incubation period as a bar chart
```{r}
fluxbar <- ggplot(fluxmean, aes(y=meanflux, x=as.factor(sample_date))) +
  geom_bar(stat="identity", fill="tomato3") +
  ylab(expression(CO[2]~flux~(mg~C~g~C^-1~d^-1))) +
  scale_x_discrete(labels=c("Period 1", "Period 2", "Period 3")) +
  geom_errorbar(aes(ymin = meanflux - seflux, ymax = meanflux + seflux), width = 0.2, size = 0.3) +
  geom_hline(yintercept=0, color="black", size=0.2) 

print(fluxbar + plottheme2)
#ggsave("C14diffplot.png", path="plots", width = 4, height = 3, dpi = 600)
```

Plot the change in flux between periods 1 and 3 vs. the change in 14C between periods 1 and 3 as scatter plot
```{r}
wide_carbon$soil_sample <- paste(wide_carbon$plot_ID, wide_carbon$layer_top)
wide_carbon$soil_sample <- paste(wide_carbon$soil_sample, wide_carbon$layer_bot, sep = "-")

difference <- wide_carbon %>% filter(sample_date != "2012-09-27") %>%  select("soil_sample", "sample_date", "X14C") %>% spread(sample_date, X14C) %>% rename("C14_per1" = "2012-09-04", "C14_per3" = "2012-10-22") %>% full_join(wide_carbon %>% filter(sample_date != "2012-09-27") %>%  select("soil_sample", "sample_date", "CO2flux_mg_g_d") %>% spread(sample_date, CO2flux_mg_g_d) %>% rename("flux_per1" = "2012-09-04", "flux_per3" = "2012-10-22")) %>% mutate(C14_diff = C14_per3 - C14_per1, flux_diff = flux_per3 - flux_per1)

flux14Cdiff <- ggplot(difference, aes(y = C14_diff, x = flux_diff)) +
  geom_point() +
  ylab(expression(Delta~Delta^14*C[CO2] ~ ("\u2030"))) +
  xlab(expression(Delta~CO[2]~flux))

print(flux14Cdiff + plottheme3)
```

Plot 14C vs. flux rate for period 1
```{r}
C14flux <- ggplot(wide_carbon %>% filter(sample_date == "2012-09-04"), aes(y = X14C, x = CO2flux_mg_g_d)) +
  geom_point() +
  ylab(expression(Delta^14*C["CO2"]~("\u2030"))) +
  xlab(expression(CO[2]~production~(mg~C~g~C^-1~d^-1)))

print(C14flux + plottheme3)
```

Plot the change in flux between periods 1 and 3 and the change in 14C between periods 1 and 3 as bar charts
```{r}
difference %>% summarize(mean(C14_diff, na.rm = T))

C14diff_bar <- ggplot(difference, aes(y = mean(C14_diff, na.rm = T), x = as.factor("1"))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = mean(C14_diff, na.rm = T) - sd(C14_diff, na.rm = T) / length(C14_diff)^0.5, ymax = mean(C14_diff, na.rm = T) + sd(C14_diff, na.rm = T) / length(C14_diff)^0.5, width = 0.2))

print(C14diff_bar)
```

For each incubated soil, plot CO2 production per in mg C day-1
```{r}
fluxplot <- ggplot(inc %>% subset(!is.na(CO2flux_total)), aes(fill=depth_increment, y=CO2flux_total, x=as.factor(sample_date))) +
  geom_bar(stat="identity", color="white") +
  ylab(expression(CO[2]~evolution~rate~(mg~C~d^-1))) +
  scale_fill_manual(values=c("#6387A6","#80AE7F",'#F2DD72'), breaks=c("Shallow","Middle","Deep"), labels=c("Shallow","Middle","Deep"), name="Depth increment") +
  geom_hline(yintercept=0, color="dimgrey", size=0.3) +
  facet_wrap( ~ plot_ID, ncol=3, labeller=as_labeller(setNames(naming[,2], naming[,1]))) + 
  scale_x_discrete(labels=c(expression(P1~(5*degree*C)), expression(P2~(10*degree*C)), expression(P3~(5*degree*C)))) 

print(fluxplot + plottheme + facettheme)
ggsave("CO2fluxplot.png", path="plots", width = 6, height = 5, dpi = 600)
```

Plot CO2 production in mg C gsoil-1 d-1
```{r}
fluxplot2 <- ggplot(inc %>% subset(!is.na(CO2flux_total)), aes(fill=depth_increment, y=CO2_production, x=as.factor(sample_date))) +
  geom_bar(stat="identity", color="white") +
  ylab(expression(CO[2]~evolution~rate~(mg~C~g["soil"]^{-1}~d^-1))) +
  scale_fill_manual(values=c("#6387A6","#80AE7F",'#F2DD72'), breaks=c("Shallow","Middle","Deep"), labels=c("Shallow","Middle","Deep"), name="Depth increment") +
  geom_hline(yintercept=0, color="dimgrey", size=0.3) +
  facet_wrap( ~ plot_ID, ncol=3, labeller=as_labeller(setNames(naming[,2], naming[,1]))) + 
  scale_x_discrete(labels=c(expression(P1~(5*degree*C)), expression(P2~(10*degree*C)), expression(P3~(5*degree*C))))

print(fluxplot2 + plottheme + facettheme)
```

plot CO2 production in mg C gC-1 d-1
```{r}
flux <- inc %>% subset(sample_type == "CO2") %>% select(-oc) %>% left_join(inc %>% subset(sample_type == "soil") %>% group_by(plot_ID, layer_top, layer_bot) %>% summarize(meanC = mean(oc))) 

fluxplot3 <- ggplot(flux %>% subset(!is.na(CO2flux_total)), aes(fill=depth_increment, y=CO2_production/meanC, x=as.factor(sample_date))) +
  geom_bar(stat="identity", color="white") +
  ylab(expression(CO[2]~evolution~rate~(mg~C~g~C^-1~d^-1))) +
  scale_fill_manual(values=c("#6387A6","#80AE7F",'#F2DD72'), breaks=c("Shallow","Middle","Deep"), labels=c("Shallow","Middle","Deep"), name="Depth increment") +
  geom_hline(yintercept=0, color="dimgrey", size=0.3) +
  facet_wrap( ~ plot_ID, ncol=3, labeller=as_labeller(setNames(naming[,2], naming[,1]))) + 
  scale_x_discrete(labels=c(expression(P1~(5*degree*C)), expression(P2~(10*degree*C)), expression(P3~(5*degree*C))))

print(fluxplot3 + plottheme + facettheme)
```

Plot the radiocarbon contents in the same format, but not with stacked bars
```{r}
C14 <- flux %>% subset(!is.na(X14C)) %>% left_join(flux %>% subset(!is.na(X14C)) %>% group_by(plot_ID, sample_date) %>% summarize(nsample = length(X14C)))

C14plot <- ggplot(C14, aes(fill=depth_increment, y=X14C, x=as.factor(sample_date))) +
  geom_bar(aes(width = .2*nsample), stat="identity", position="dodge") +
  ylab(expression(Delta^14*C[CO2] ~ ("\u2030"))) +
  scale_fill_manual(values=c("#6387A6","#80AE7F",'#F2DD72'), breaks=c("Shallow","Middle","Deep"), labels=c("Shallow","Middle","Deep"), name="Depth increment") +
  geom_hline(yintercept=0, color="dimgrey", size=0.3) +
  facet_wrap( ~ plot_ID, ncol=3, labeller=as_labeller(setNames(naming[,2], naming[,1]))) + 
  scale_x_discrete(labels=c(expression(P1~(5*degree*C)), expression(P2~(10*degree*C)), expression(P3~(5*degree*C))))

print(C14plot + plottheme + facettheme)
```

Plot the change in radiocarbon between periods 1 and 2 and periods 1 and 3
```{r}
C14wide <- C14 %>% select(plot_ID, sample_date, X14C, depth_increment) %>% spread(key=sample_date,value=X14C) %>% rename(P3 = "2012-10-22", P2 = "2012-09-27", P1 = "2012-09-04") %>% mutate(P3P1 = P3 - P1, P2P1 = P2 - P1)

C14long <- C14wide %>% select(plot_ID, depth_increment, P3P1, P2P1) %>% gather(key="Period", value="C14diff", 3:4)

#Box plot, only shallow and deep increments
C14box <- ggplot(C14long %>% subset(depth_increment != "Middle"), aes(fill=depth_increment, y=C14diff, x=Period)) +
  geom_hline(yintercept=0, color="black", size=0.3) +
  geom_boxplot(position = position_dodge(0.8)) +
  scale_fill_manual(values=c("#E5A32F","tomato3"), name="Depth increment", labels=c("Shallow","Deep")) +
  ylab(expression("Change in"~Delta^14*C[CO2] ~ ("\u2030"))) +
  scale_x_discrete(labels=c("Periods 1 to 2", "Periods 1 to 3")) 

print(C14box + plottheme)

#Bar chart, only shallow and deep increments
C14depths <- C14long %>% subset(depth_increment != "Middle" & !is.na(C14diff)) %>% group_by(Period, depth_increment) %>% summarize(meanC14diff = mean(C14diff), sdC14diff = sd(C14diff), nC14diff = length(C14diff)) %>% mutate(seC14diff = sdC14diff/nC14diff^0.5)

C14bar <- ggplot(C14depths, aes(fill = depth_increment, y=meanC14diff, x=Period)) +
  geom_bar(stat="identity", position=position_dodge(0.8), width=0.75) +
  scale_fill_manual(values=c("#E5A32F","tomato3"), name="Depth increment", labels=c("Shallow","Deep")) +
  ylab(expression("Change in"~Delta^14*C[CO2] ~ ("\u2030"))) +
  scale_x_discrete(labels=c("Periods 1 to 2", "Periods 1 to 3")) +
  geom_errorbar(aes(ymin = meanC14diff - seC14diff, ymax = meanC14diff + seC14diff), position = position_dodge(0.8), width = 0.2, size = 0.4) +
  geom_hline(yintercept=0, color="black", size=0.3) 
print(C14bar + plottheme)

#Box plot, all increments
C14box2 <- ggplot(C14long, aes(y=C14diff, x=Period)) +
  geom_hline(yintercept=0, color="black", size=0.3) +
  geom_boxplot(fill="tomato3") +
  ylab(expression("Change in"~Delta^14*C[CO2] ~ ("\u2030"))) +
  scale_x_discrete(labels=c("Periods 1 to 2", "Periods 1 to 3")) 

print(C14box2 + plottheme2)
ggsave("C14diffbox.png", path="plots", width = 4, height = 3, dpi = 600)

#Bar chart all increments
C14summary <- C14long %>% subset(!is.na(C14diff)) %>% group_by(Period) %>% summarize(meanC14diff = mean(C14diff), sdC14diff = sd(C14diff), nC14diff = length(C14diff)) %>% mutate(seC14diff = sdC14diff/nC14diff^0.5)

C14bar2 <- ggplot(C14summary, aes(y=meanC14diff, x=Period)) +
  geom_bar(stat="identity", fill="tomato3", width=0.75) +
  ylab(expression("Change in"~Delta^14*C[CO2] ~ ("\u2030"))) +
  scale_x_discrete(labels=c("Periods 1 to 2", "Periods 1 to 3")) +
  geom_errorbar(aes(ymin = meanC14diff - seC14diff, ymax = meanC14diff + seC14diff), width = 0.2, size = 0.3) +
  geom_hline(yintercept=0, color="black", size=0.2) 

print(C14bar2 + plottheme2)
ggsave("C14diffplot.png", path="plots", width = 4, height = 3, dpi = 600)
```

Scatterplot with, periods 1 and 2
```{r}
flux_12 <- ggplot(wide_carbon %>% filter(sample_date != "2012-10-22"), aes(y = log(CO2flux_mg_g_d), x = sample_date, group = soil_sample)) +
  geom_point() +
  geom_line(aes(group = soil_sample))

print(flux_12)

flux_13 <- ggplot(wide_carbon %>% filter(sample_date != "2012-09-27"), aes(y = log(CO2flux_mg_g_d), x = sample_date, group = soil_sample)) +
  geom_point() +
  geom_line(aes(group = soil_sample))

print(flux_13)

C14_12 <- ggplot(wide_carbon %>% filter(sample_date != "2012-10-22"), aes(y = X14C, x = sample_date, group = soil_sample)) +
  geom_point() +
  geom_line(aes(group = soil_sample))

print(C14_12)

C14_13 <- ggplot(wide_carbon %>% filter(sample_date != "2012-09-27"), aes(y = X14C, x = sample_date, group = soil_sample)) +
  geom_point() +
  geom_line(aes(group = soil_sample))

print(C14_13)
```

Scatterplot Scatterplot with, periods 1 and 2, normalized to period 1 value
```{r}
wide_carbon <- wide_carbon %>% full_join(wide_carbon %>% filter(sample_date == "2012-09-04") %>% select("soil_sample", "X14C", "CO2flux_mg_g_d") %>% rename("baseline.14C" = "X14C", "baseline.flux" = "CO2flux_mg_g_d"))

xlabels <- c("Period 1", "Period 2")
#xlabels <- c(expression(Period~1~(5*degree*C)), expression(Period~2~(10*degree*C)))


fluxnorm_12 <- ggplot(wide_carbon %>% filter(sample_date != "2012-10-22"), aes(y = CO2flux_mg_g_d - baseline.flux, x = as.numeric(as.factor(sample_date)), group = soil_sample)) +
  geom_hline(yintercept = 0, alpha = 0.5) +
  geom_point(color = "steelblue4", alpha = 0.7) +
  geom_line(aes(group = soil_sample), color = "steelblue4", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2), limits = c(.95, 2.05)) +
  ylab(expression("Change in"~CO[2]~production~(mg~C~g~C^-1~d^-1))) 

print(fluxnorm_12 + plottheme4)

xlabels <- c("Period 1", "Period 3")
#xlabels <- c(expression(Period~1~(5*degree*C)), expression(Period~3~(5*degree*C)))


fluxnorm_13 <- ggplot(wide_carbon %>% filter(sample_date != "2012-09-27"), aes(y = CO2flux_mg_g_d - baseline.flux, x = as.numeric(as.factor(sample_date)), group = soil_sample)) +
  geom_hline(yintercept = 0, alpha = 0.5) +
  geom_point(color = "steelblue4", alpha = 0.7) +
  geom_line(aes(group = soil_sample), color = "steelblue4", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2), limits = c(.95, 2.05)) +
  ylab(expression("Change in"~CO[2]~production~(mg~C~g~C^-1~d^-1))) 

print(fluxnorm_13 + plottheme4)

xlabels <- c("Incubation 1 \n (5°C)", "Incubation 2 \n (10°C)", "Incubation 3 \n (5°C)")
#xlabels <- c(expression(Period~1~(5*degree*C)), expression(Period~2~(10*degree*C)), expression(Period~3~(5*degree*C)))


fluxnorm_123 <- ggplot(wide_carbon, aes(y = (CO2flux_mg_g_d - baseline.flux) * 1000, x = as.numeric(as.factor(sample_date)), group = soil_sample)) +
  geom_hline(yintercept = 0, size = 0.25) +
  geom_point(color = "#5272A3", alpha = 0.7) +
  geom_line(aes(group = soil_sample), color = "#5272A3", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2, 3), limits = c(1, 3)) +
  ylab(expression(atop("Change in"~CO[2]~production, (mu*g~C~g~C^-1~d^-1)))) 

print(fluxnorm_123 + plottheme4)
```

Line plots of the change in 14C between incubaiton periods
```{r}
xlabels <- c("Period 1", "Period 2")
#xlabels <- c(expression(Period~1~(5*degree*C)), expression(Period~2~(10*degree*C)))


C14norm_12 <- ggplot(wide_carbon %>% filter(sample_date != "2012-10-22"), aes(y = X14C - baseline.14C, x = as.numeric(as.factor(sample_date)), group = soil_sample)) +
  geom_hline(yintercept = 0, alpha = 0.5) +
  geom_point(color = "chocolate4", alpha = 0.5) +
  geom_line(aes(group = soil_sample), color = "chocolate", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2), limits = c(.95, 2.05)) +
  ylab(expression("Change in"~Delta^14*C[CO2]~("\u2030"))) 

print(C14norm_12 + plottheme4)

xlabels <- c("Period 1", "Period 3")
#xlabels <- c(expression(Period~1~(5*degree*C)), expression(Period~3~(5*degree*C)))


C14norm_13 <- ggplot(wide_carbon %>% filter(sample_date != "2012-09-27"), aes(y = X14C - baseline.14C, x = as.numeric(as.factor(sample_date)), group = soil_sample, label = sample_date)) +
  geom_hline(yintercept = 0, alpha = 0.5) +
  geom_point(color = "chocolate4", alpha = 0.5) +
  geom_line(aes(group = soil_sample), color = "chocolate", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2), limits = c(.95, 2.05)) +
  ylab(expression("Change in"~Delta^14*C[CO2]~("\u2030"))) 

print(C14norm_13 + plottheme4)

xlabels <- c("Incubation 1 \n (5°C)", "Incubation 2 \n (10°C)", "Incubation 3 \n (5°C)")

C14norm_123 <- ggplot(wide_carbon, aes(y = X14C - baseline.14C, x = as.numeric(as.factor(sample_date)), group = soil_sample)) +
  geom_hline(yintercept = 0, size = 0.25) +
  #geom_point(color = "tomato4", alpha = 0.5) +
  geom_point(color = "#CC5B0F", alpha = 0.5) +
  geom_line(aes(group = soil_sample), color = "#CC5B0F", alpha = 0.4) +
  scale_x_continuous(labels = xlabels, breaks = c(1, 2, 3)) +
  #ylab(expression("Change in"~Delta^14*C[CO2]~("\u2030"))) 
  ylab(expression(atop("Change in"~Delta^14*C[CO2], ("\u2030"))))
  #labs(x='really long label \n with a return')

print(C14norm_123 + plottheme4)
```

Arrange the flux and 14C plots
```{r}
p1 <- fluxnorm_12 + plottheme4 
p2 <- fluxnorm_13 + plottheme4
#p3 <- fluxnorm_123 + plottheme4 + ggtitle('a') + theme(axis.title.y = element_text(vjust=-0.2)) + theme(plot.margin = unit(c(3, 7, 3, 1), "mm"))
p3 <- fluxnorm_123 + plottheme4 + ggtitle('a') + theme(plot.margin = unit(c(3, 7, 3, 1), "mm")) + theme(axis.title.y = element_text(vjust=-0.1)) 
p4 <- C14norm_12 + plottheme4 
p5 <- C14norm_13 + plottheme4
#p6 <- C14norm_123 + plottheme4 + ggtitle('b') + theme(axis.title.y = element_text(vjust=0.65)) + theme(plot.margin = unit(c(3, 7, 3, 4.3), "mm"))
p6 <- C14norm_123 + plottheme4 + ggtitle('b') + theme(plot.margin = unit(c(3, 7, 3, 0.4), "mm")) + theme(axis.title.y = element_text(vjust=-0.1)) 

combo1 <- grid.arrange(p1, p2, p4, p5, ncol=2, nrow=2, heights = c(4,4))

combo2 <- grid.arrange(p3, p6, ncol=1, nrow=2, widths =c(8))

ggsave("fluxC14_1.png", combo1, path="plots", width = 6,height = 5.25,dpi = 300)
ggsave("fluxC14_2.png", combo2, path="plots", width = 4,height = 5.33,dpi = 300)
```
