---
title: "Delta analysis for 2012 Radiocarbon incubations"
author: "Lydia Vaughn"
date: "2018-01-18"
output: html_document
---

Data: radiocarbon_incubation_Barrow_2012.csv includes CO2 flux rates and radiocarbon values from incubated soils.  File and data description can be accessed at http://dx.doi.org/10.5440/1364062
```{r}
inc <- read.csv('data/radiocarbon_incubation_Barrow_2012.csv', stringsAsFactors=F)
```

Packages
```{r}
library(lme4)
library(lmerTest)
library(gridExtra)
library(tidyverse)
library(car)
```

Limit the dataframe to just CO2 from this experiment and make column for soil sample identifier
```{r}
inc2012 <- inc %>% filter(observation_date=="8/14/12" & sample_type=="CO2" &!is.na(X14C))  %>% mutate(soil_sample = paste(plot_ID,layer_top))
```

Calculate Delta2 and Delta3 for each sample
```{r}
BulkDelta <- inc2012 %>% select(soil_sample,plot_ID,CO2_production,sample_date) %>%  spread(key=sample_date,value=CO2_production) %>% rename(T3 = "10/22/12", T2 = "9/27/12", T1 = "9/4/12") %>% mutate(Delta2 = (T2 - T1)/T1*100, Delta2b = (T2 - T3)/T3*100, Delta3 = (T3 - T1)/T1*100)
```

Design a theme for all plots
```{r}
plottheme <- theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank()) +
  theme(axis.text = element_text(color="black", size=10)) +
  theme(axis.title = element_text(size=12)) +
  theme(plot.title = element_text(colour = "black", size=10, hjust = -0.15, face = "bold")) 

```

Plot Delta2 vs Delta3 for the bulk data
```{r}
BulkPlot <- ggplot(BulkDelta, aes(y=Delta2, x=Delta3)) +
  geom_point(size=2, color="#27A36B", alpha = 0.8) +
  ylab(expression(Delta[2]~"(%)")) +
  xlab(expression(Delta[3]~"(%)")) +
  xlim(-75, 25) +
  ylim(-50,50) 

BulkPlot + plottheme 
```

Do the same for Delta2b and Delta3
```{r}
BulkPlotb <- ggplot(BulkDelta, aes(y=Delta2b, x=Delta3)) +
  geom_point(size=2, color="#27A36B") +
  ylab(expression(Delta["2,3"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  xlim(-80, 0) +
  ylim(20,100) 

BulkPlotb + plottheme
```

Use a linear mixed effects model to find the linear relationship between Delta2 and Delta3
```{r}
BulkModel <- lmer(Delta2 ~ Delta3 + (1|plot_ID), data=BulkDelta)
summary(BulkModel)

#Diagnostic tests of model assumptions
plot(fitted(BulkModel), residuals(BulkModel), xlab = "Fitted", ylab = "Residuals")
plot(BulkDelta[!is.na(BulkDelta$Delta3),]$Delta3, residuals(BulkModel), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(BulkModel))
qqline(residuals(BulkModel))
```

Do the same for Delta2b and Delta3
```{r}
BulkModelb <- lmer(Delta2b ~ Delta3 + (1|plot_ID), data=BulkDelta)
summary(BulkModelb)

#Diagnostic tests of model assumptions
plot(fitted(BulkModelb), residuals(BulkModelb), xlab = "Fitted", ylab = "Residuals")
plot(BulkDelta[!is.na(BulkDelta$Delta3),]$Delta3, residuals(BulkDelta), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(BulkModelb))
qqline(residuals(BulkModelb))

```

Add trend line to BulkPlot
```{r}
BulkPlot_final <- ggplot(BulkDelta, aes(y=Delta2, x=Delta3)) +
  #geom_abline(slope=summary(BulkModel)$coefficients[2,1], intercept=summary(BulkModel)$coefficients[1,1], colour="#27A36B", alpha = 0.6, size = 1) +
  stat_smooth(geom="line", alpha=0.6, size=1, method = "lm", se = FALSE, fullrange = T, color="#27A36B") +
geom_point(size=3, alpha = 0.8, color="#27A36B") +
  ylab(expression(Delta["1,2"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  xlim(-75, 25) +
  ylim(-50,50) +
  plottheme 

print(BulkPlot_final)

ggsave("BulkPlot.png", path="plots", width = 4,height = 3.93,dpi = 300)
```

Do the same for BulkPlotb
```{r}
BulkPlotb_final <- BulkPlotb + 
  plottheme +
  #geom_abline(slope=summary(BulkModelb)$coefficients[2,1], intercept=summary(BulkModelb)$coefficients[1,1], lty="dashed", colour="dimgrey") 
  stat_smooth(geom="line", alpha=0.6, size=1, method = "lm", se = FALSE, fullrange = T, color="#27A36B") 

print(BulkPlotb_final)

ggsave("BulkPlotb.png", path="plots", width = 4,height = 3.93,dpi = 300)
```

Partition bulk CO2 fluxes into passive and active fractions with turnover times of (a) 50 and 5000 years and (b) 20 and 10000 years
```{r}
part_50_5000 <- inc2012 %>% mutate(f_active = (X14C + 360)/(360 + 146), f_passive = 1 - f_active, CO2_production_active = f_active * CO2_production, CO2_production_passive = f_passive * CO2_production) 

part_20_10000 <- inc2012 %>% mutate(f_active = (X14C + 524)/(524 + 137), f_passive = 1 - f_active, CO2_production_active = f_active * CO2_production, CO2_production_passive = f_passive * CO2_production) 
```

Calculate Delta2, Delta2b, and Delta3 for each set of partitioned fluxes
```{r}
active_50_5000 <- part_50_5000 %>% select(soil_sample,plot_ID,CO2_production_active,sample_date) %>%  spread(key=sample_date,value=CO2_production_active) %>% rename(T3 = "10/22/12", T2 = "9/27/12", T1 = "9/4/12") %>% mutate(Delta2 = (T2 - T1)/T1*100, Delta2b = (T2 - T3)/T3*100, Delta3 = (T3 - T1)/T1*100, pool = "Active") %>% select(soil_sample, plot_ID, Delta2, Delta2b, Delta3, pool)

passive_50_5000 <- part_50_5000 %>% select(soil_sample,plot_ID,CO2_production_passive,sample_date) %>%  spread(key=sample_date,value=CO2_production_passive) %>% rename(T3 = "10/22/12", T2 = "9/27/12", T1 = "9/4/12") %>% mutate(Delta2 = (T2 - T1)/T1*100, Delta2b = (T2 - T3)/T3*100, Delta3 = (T3 - T1)/T1*100, pool = "Passive") %>% select(soil_sample, plot_ID, Delta2, Delta2b, Delta3, pool)

PoolsDelta_50_5000 <- active_50_5000 %>% full_join(passive_50_5000)

active_20_10000 <- part_20_10000 %>% select(soil_sample,plot_ID,CO2_production_active,sample_date) %>%  spread(key=sample_date,value=CO2_production_active) %>% rename(T3 = "10/22/12", T2 = "9/27/12", T1 = "9/4/12") %>% mutate(Delta2 = (T2 - T1)/T1*100, Delta2b = (T2 - T3)/T3*100, Delta3 = (T3 - T1)/T1*100, pool = "Active") %>% select(soil_sample, plot_ID, Delta2, Delta2b, Delta3, pool)

passive_20_10000 <- part_20_10000 %>% select(soil_sample,plot_ID,CO2_production_passive,sample_date) %>%  spread(key=sample_date,value=CO2_production_passive) %>% rename(T3 = "10/22/12", T2 = "9/27/12", T1 = "9/4/12") %>% mutate(Delta2 = (T2 - T1)/T1*100, Delta2b = (T2 - T3)/T3*100, Delta3 = (T3 - T1)/T1*100, pool = "Passive") %>% select(soil_sample, plot_ID, Delta2, Delta2b, Delta3, pool)

PoolsDelta_20_10000 <- active_20_10000 %>% full_join(passive_20_10000)
```

Plot Delta2 vs Delta3 for the partitioned data
```{r}
#Turnover times = 50y and 5,000y

legendtheme <- theme(legend.title = element_text(size=9)) +
  theme(legend.text = element_text(size=8)) +
  theme(legend.position = c(.7, .25)) +
  theme(legend.key.size = unit(0.5, "cm")) +
  theme(legend.background = element_rect(color=NA, fill=NA))

PoolsPlot_50_5000 <- ggplot(PoolsDelta_50_5000, aes(colour=pool, shape=pool, name="Carbon pool", y=as.numeric(Delta2), x=as.numeric(Delta3))) +
  geom_point(size=2) +
  ylab(expression(Delta["1,2"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  scale_colour_manual(values=c("#4074DC","#FCAA3D"), name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  scale_shape_discrete(name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  xlim(-75, 25) +
  ylim(-50,50) 

PoolsPlot_50_5000 + plottheme + legendtheme

#Turnover times = 20y and 10,000y
PoolsPlot_20_10000 <- ggplot(PoolsDelta_20_10000, aes(colour=pool, shape=pool, name="Carbon pool", y=as.numeric(Delta2), x=as.numeric(Delta3))) +
  geom_point(size=2) +
  ylab(expression(Delta["1,2"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  scale_colour_manual(values=c("mediumseagreen","mediumslateblue"), name="Carbon pool", labels=c("Active (TT = 20 y)", "Passive (TT = 10,000 y)")) +
  scale_shape_discrete(name="Carbon pool", labels=c("Active (TT = 20 y)", "Passive (TT = 10,000 y)")) +
  xlim(-75, 25) +
  ylim(-50,50) 

PoolsPlot_20_10000 + plottheme + legendtheme
```

Do the same with Delta2b vs Delta3
```{r}
legendthemeb <- theme(legend.title = element_text(size=8)) +
  theme(legend.text = element_text(size=6)) +
  theme(legend.position = c(.4, .25), panel.background = element_blank()) +
  theme(legend.key.size = unit(0.5, "cm")) +
  theme(legend.background = element_rect(color=NA, fill=NA))


#Turnover times = 50y and 5,000y
PoolsPlotb_50_5000 <- ggplot(PoolsDelta_50_5000, aes(colour=pool, shape=pool, name="Carbon pool", y=as.numeric(Delta2b), x=as.numeric(Delta3))) +
  geom_point(size=2) +
  ylab(expression(Delta["2,3"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  scale_colour_manual(values=c("#4074DC","#FCAA3D"), name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  scale_shape_discrete(name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  xlim(-80, 0) +
  ylim(20,100) 

PoolsPlotb_50_5000 + plottheme + legendthemeb

#Turnover times = 20y and 10,000y
PoolsPlotb_20_10000 <- ggplot(PoolsDelta_20_10000, aes(colour=pool, shape=pool, name="Carbon pool", y=as.numeric(Delta2b), x=as.numeric(Delta3))) +
  geom_point(size=2) +
  ylab(expression(Delta["2,3"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  scale_colour_manual(values=c("mediumseagreen","mediumslateblue"), name="Carbon pool", labels=c("Active (TT = 20 y)", "Passive (TT = 10,000 y)")) +
  scale_shape_discrete(name="Carbon pool", labels=c("Active (TT = 20 y)", "Passive (TT = 10,000 y)")) +
  xlim(-80, 0) +
  ylim(20,100) 

PoolsPlotb_20_10000 + plottheme + legendthemeb
```

Use Delta2 to test whether the pools have different temprature senstivities using turnover times of 50 and 5000 years
```{r}
#Model including pool as a fix effect
PoolsModel_50_5000_full <- lmer(Delta2 ~ Delta3 + pool + (1|plot_ID/soil_sample), data=PoolsDelta_50_5000, REML=F)
summary(PoolsModel_50_5000_full)

plot(fitted(PoolsModel_50_5000_full), residuals(PoolsModel_50_5000_full), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_50_5000[!is.na(PoolsDelta_50_5000$Delta3),]$Delta3, residuals(PoolsModel_50_5000_full), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModel_50_5000_full))
qqline(residuals(PoolsModel_50_5000_full))

#Model without pool as fixed effect
PoolsModel_50_5000_reduced <- lmer(Delta2 ~ Delta3 + (1|plot_ID/soil_sample), data=PoolsDelta_50_5000, REML=F)
summary(PoolsModel_50_5000_reduced)

plot(fitted(PoolsModel_50_5000_reduced), residuals(PoolsModel_50_5000_reduced), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_50_5000[!is.na(PoolsDelta_50_5000$Delta3),]$Delta3, residuals(PoolsModel_50_5000_reduced), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModel_50_5000_reduced))
qqline(residuals(PoolsModel_50_5000_reduced))

#Likelihood ratio test to determine whether pool is a significant fixed effect
anova(PoolsModel_50_5000_full, PoolsModel_50_5000_reduced)
```

Do the same with Delta2b and Delta3
```{r}
#Model including pool as a fix effect
PoolsModelb_50_5000_full <- lmer(Delta2b ~ Delta3 + pool + (1|plot_ID/soil_sample), data=PoolsDelta_50_5000, REML=F)
summary(PoolsModelb_50_5000_full)

plot(fitted(PoolsModelb_50_5000_full), residuals(PoolsModelb_50_5000_full), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_50_5000[!is.na(PoolsDelta_50_5000$Delta3),]$Delta3, residuals(PoolsModelb_50_5000_full), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModelb_50_5000_full))
qqline(residuals(PoolsModelb_50_5000_full))

#Model without pool as fixed effect
PoolsModelb_50_5000_reduced <- lmer(Delta2b ~ Delta3 + (1|plot_ID/soil_sample), data=PoolsDelta_50_5000, REML=F)
summary(PoolsModelb_50_5000_reduced)

plot(fitted(PoolsModelb_50_5000_reduced), residuals(PoolsModelb_50_5000_reduced), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_50_5000[!is.na(PoolsDelta_50_5000$Delta3),]$Delta3, residuals(PoolsModelb_50_5000_reduced), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModelb_50_5000_reduced))
qqline(residuals(PoolsModelb_50_5000_reduced))

#Likelihood ratio test to determine whether pool is a significant fixed effect
anova(PoolsModelb_50_5000_full, PoolsModelb_50_5000_reduced)
```

Use Delta2 and Delta3 to test whether the pools have different temprature senstivities using turnover times of 20 and 10000 years
```{r}
#Model including pool as a fix effect
PoolsModel_20_10000_full <- lmer(Delta2 ~ Delta3 + pool + (1|plot_ID/soil_sample), data=PoolsDelta_20_10000, REML=F)
summary(PoolsModel_20_10000_full)

plot(fitted(PoolsModel_20_10000_full), residuals(PoolsModel_20_10000_full), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_20_10000[!is.na(PoolsDelta_20_10000$Delta3),]$Delta3, residuals(PoolsModel_20_10000_full), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModel_20_10000_full))
qqline(residuals(PoolsModel_20_10000_full))

#Model without pool as fixed effect
PoolsModel_20_10000_reduced <- lmer(Delta2 ~ Delta3 + (1|plot_ID/soil_sample), data=PoolsDelta_20_10000, REML=F)
summary(PoolsModel_20_10000_reduced)

plot(fitted(PoolsModel_20_10000_reduced), residuals(PoolsModel_20_10000_reduced), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_20_10000[!is.na(PoolsDelta_20_10000$Delta3),]$Delta3, residuals(PoolsModel_20_10000_reduced), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModel_20_10000_reduced))
qqline(residuals(PoolsModel_20_10000_reduced))

#Likelihood ratio test to determine whether pool is a significant fixed effect
anova(PoolsModel_20_10000_full, PoolsModel_20_10000_reduced)
```

Do the same with Delta2b and Delta3
```{r}
#Model including pool as a fix effect
PoolsModelb_20_10000_full <- lmer(Delta2b ~ Delta3 + pool + (1|plot_ID/soil_sample), data=PoolsDelta_20_10000, REML=F)
summary(PoolsModelb_20_10000_full)

plot(fitted(PoolsModelb_20_10000_full), residuals(PoolsModelb_20_10000_full), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_20_10000[!is.na(PoolsDelta_20_10000$Delta3),]$Delta3, residuals(PoolsModelb_20_10000_full), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModelb_20_10000_full))
qqline(residuals(PoolsModelb_20_10000_full))

#Model without pool as fixed effect
PoolsModelb_20_10000_reduced <- lmer(Delta2b ~ Delta3 + (1|plot_ID/soil_sample), data=PoolsDelta_20_10000, REML=F)
summary(PoolsModelb_20_10000_reduced)

plot(fitted(PoolsModelb_20_10000_reduced), residuals(PoolsModelb_20_10000_reduced), xlab = "Fitted", ylab = "Residuals")
plot(PoolsDelta_20_10000[!is.na(PoolsDelta_20_10000$Delta3),]$Delta3, residuals(PoolsModelb_20_10000_reduced), xlab = expression(Delta["1,3"]), ylab = "Residuals")
qqnorm(residuals(PoolsModelb_20_10000_reduced))
qqline(residuals(PoolsModelb_20_10000_reduced))

#Likelihood ratio test to determine whether pool is a significant fixed effect
anova(PoolsModelb_20_10000_full, PoolsModelb_20_10000_reduced)
```

Add trend lines to the pools plots using Delta2 and Delta3
```{r}
#Turnover times = 50y and 5,000y
PoolsPlot_50_5000_final <- ggplot(PoolsDelta_50_5000, aes(colour=pool, shape=pool, name="Carbon pool", y=as.numeric(Delta2), x=as.numeric(Delta3))) +
  #geom_abline(slope=summary(PoolsModel_50_5000_reduced)$coefficients[2,1], intercept=summary(PoolsModel_50_5000_reduced)$coefficients[1,1], lty="dashed", colour="dimgrey") +
  stat_smooth(geom="line", alpha=0.8, size=1, method = "lm", se = FALSE, fullrange = T) +
  geom_point(size=3, alpha = 0.7) +
  ylab(expression(Delta["1,2"]~"(%)")) +
  xlab(expression(Delta["1,3"]~"(%)")) +
  scale_colour_manual(values=c("#4074DC","#FCAA3D"), name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  scale_shape_discrete(name="Carbon pool", labels=c("Active (TT = 50 y)", "Passive (TT = 5,000 y)")) +
  xlim(-75, 25) +
  ylim(-50,50) +
  plottheme + 
  legendtheme 

print(PoolsPlot_50_5000_final)
ggsave("PoolsPlot_50_5000.png", path="plots", width = 4,height = 3.93, dpi = 300)

#Turnover times = 20y and 10,000y
PoolsPlot_20_10000_final <- PoolsPlot_20_10000 + 
  plottheme + 
  legendtheme +
  #geom_abline(slope=summary(PoolsModel_20_10000_reduced)$coefficients[2,1], intercept=summary(PoolsModel_20_10000_reduced)$coefficients[1,1], lty="dashed", colour="dimgrey")
  stat_smooth(geom="line", alpha=0.8, size=1, method = "lm", se = FALSE, fullrange = T) 

print(PoolsPlot_20_10000_final)
ggsave("PoolsPlot_20_10000.png", path="plots", width = 4,height = 3.93,dpi = 300)
```

Do the same with the pools plots using Delta2b and Delta3
```{r}
#Turnover times = 50y and 5,000y
PoolsPlotb_50_5000_final <- PoolsPlotb_50_5000 + 
    plottheme + 
    legendthemeb +
    #geom_abline(slope=summary(PoolsModelb_50_5000_reduced)$coefficients[2,1], intercept=summary(PoolsModelb_50_5000_reduced)$coefficients[1,1], lty="dashed", colour="dimgrey")
    stat_smooth(geom="line", alpha=0.8, size=1, method = "lm", se = FALSE, fullrange = T) 

print(PoolsPlotb_50_5000_final)
ggsave("PoolsPlotb_50_5000.png", path="plots", width = 4,height = 3.93, dpi = 300)


#Turnover times = 20y and 10,000y
PoolsPlotb_20_10000_final <- PoolsPlotb_20_10000 + 
    plottheme + 
    legendthemeb +
    #geom_abline(slope=summary(PoolsModelb_20_10000_reduced)$coefficients[2,1], intercept=summary(PoolsModelb_20_10000_reduced)$coefficients[1,1], lty="dashed", colour="dimgrey") 
    stat_smooth(geom="line", alpha=0.8, size=1, method = "lm", se = FALSE, fullrange = T) 

print(PoolsPlotb_20_10000_final)
ggsave("PoolsPlotb_20_10000.png", path="plots", width = 4,height = 3.93,dpi = 300)
```

Arrange the plots for publication
```{r}
p1 <- BulkPlot_final + ggtitle('a') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p2 <- PoolsPlot_50_5000_final + ggtitle('b') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
combo <- grid.arrange(p1, p2, ncol=2, widths=c(4,4))
ggsave("CombinedPlot.png", combo, path="plots", width = 8,height = 4,dpi = 600)

p3 <- BulkPlotb_final + ggtitle('a') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p4 <- PoolsPlotb_50_5000_final + ggtitle('b') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
combob <- grid.arrange(p3, p4, ncol=2, widths=c(4,4))
ggsave("CombinedPlotb.png", combob, path="plots", width = 8,height = 4,dpi = 600)

p5 <- PoolsPlot_50_5000_final + ggtitle('a') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p6 <- PoolsPlot_20_10000_final + ggtitle('b') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
comboc <- grid.arrange(p5, p6, ncol=2, widths=c(4,4))
ggsave("CombinedPlotc.png", comboc, path="plots", width = 8,height = 4,dpi = 600)

p7 <- BulkPlotb_final + ggtitle('b') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p8 <- PoolsPlot_50_5000_final + ggtitle('c') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p9 <- PoolsPlotb_50_5000_final + ggtitle('d') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
combod <- grid.arrange(p1, p7, p8, p9, ncol=2, widths=c(4,4))
ggsave("CombinedPlotd.png", combod, path="plots", width = 6,height = 6,dpi = 600)
```

Power analysis of likelihood ratio test of pool-specific temperature sensitivities version 2
```{r}
active <- lm(Delta2 ~ Delta3, data=PoolsDelta_50_5000 %>% filter(pool == "Active"))
summary(active)
passive <- lm(Delta2 ~ Delta3, data=PoolsDelta_50_5000 %>% filter(pool == "Passive"))
summary(passive)

summary(active)
summary(passive)

nsim <- 400

N = 22
a = 41.54385
a.act = 38.79211
a.pass = 40.88875
b.act = 1.14658
b.pas = 1.12149
b = 1.19345
sd.D2.act = 24.76824
sd.D2.pas = 17.25242
sd.act = 0.08563
sd.pas = 0.09861
set.seed(1)

power.int <- data.frame(Q10.difference=seq(0, 0.2, 0.01), power=NA) 

for(j in 1:length(power.int$Q10.difference)) {
  
  a.diff <- power.int$Q10.difference[j]

  a.act <- (((1 + a/100)^2 - a.diff/2)^0.5 - 1) * 100
  a.pas <- (((1 + a/100)^2 + a.diff/2)^0.5 - 1) * 100

  nsim = 400
  
  pval = numeric(nsim)

  for(i in 1:nsim) {
    
    D3.act = rnorm(N, mean = -36.66068, sd = 21.81299)
    D3.pas = rnorm(N, mean = -22.79575, sd = 13.31881)

    active <- data.frame(Pool = "Active", Delta3 = D3.act, a = rnorm(22, mean = a.act, sd = 3.62758), b = rnorm(22, mean = b, sd = 0.08563)) %>% mutate(Delta2 = a + b * Delta3)
  
    passive <- data.frame(Pool = "Passive", Delta3 = D3.pas, a = rnorm(22, mean = a.pas, sd = 2.58586), b = rnorm(22, mean = b, sd = 0.09861)) %>% mutate(Delta2 = a + b * Delta3)

    df <- rbind(passive, active)

    model_full <- lm(Delta2 ~ Delta3 + Pool, data=df)
    model_red <- lm(Delta2 ~ Delta3, data = df)
    anova(model_full, model_red)
  
    pval[i] = anova(model_full, model_red)[2, "Pr(>F)"]
  }
    testplot <- ggplot(df, aes(x = Delta3, y = Delta2, color = Pool)) +
    theme_bw() +
    stat_smooth(geom="line", alpha=0.8, size=1, method = "lm", se = FALSE, fullrange = T) +
    geom_point(size=3, alpha = 0.7) +
    annotate("text", label = paste("Q10 difference =", a.diff), x = -50, y = 42, color = "black") +
    ylab(expression(Delta["1,2"]~"(%)")) +
    xlab(expression(Delta["1,3"]~"(%)")) +
    scale_colour_manual(values=c("#4074DC","#FCAA3D"), name="Carbon pool", labels=c("Active", "Passive")) +
    scale_shape_discrete(name="Carbon pool", labels=c("Active", "Passive")) +
    xlim(-75, 25) +
    ylim(-50,50) +
    plottheme + 
    legendtheme
   
  print(testplot)
 
  assign(paste("testplot", a.diff, sep="_"), testplot)

  print(mean(abs(residuals(model_red))))

  power.int$power[j] = sum(pval < 0.05)/nsim
}

p10 <- testplot_0 + ggtitle('a') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p11 <- testplot_0.12 + ggtitle('b') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
p12 <- testplot_0.19 + ggtitle('c') + theme(plot.margin = unit(c(0.5,0.5,0.5,0.5), "cm"))
comboe <- grid.arrange(p10, p11, p12, ncol=1, nrow=3, heights=c(4,4,4), widths=4)

ggsave("CombinedPlote.png", comboe, path="plots", width = 4,height = 9,dpi = 600)


print(power.int)
#This shows that our test has a power of 0.8 (will detect a significant difference between pools at least 80% of the time) when there is a difference in Q10 of 0.12 or greater
```
