---
title: "TT calculation"
author: "Lydia Vaughn"
date: "14/03/2017"
output: html_document
---

Create 14C curve for steady state post-bomb system for different turnover times

```{r}
atm <- read.csv('data/atmospheric_14C.csv', header=T, sep=',', na.strings=c('','no data'), fill=T, quote='', stringsAsFactors=F)
```

1. Set parameters
```{r}
# turnover times (in years) for which you want to calculate Delta14C. 
years <- c(1:10, seq(100, 10000, 100))

# max end of range of carbon residence times in plants, in years (0 years will be used as the minimum by default)
plant_res <- 5

# years your sample were collected
collyear <- c(2012, 2013, 2014)
```

2. Make data frames for each specified turnover time and compile them in a list called Turnover
```{r}
#atm_res <- atm_res[atm_res$name!="NA",]
#TT1 <- TT1[TT1$name!="NA",]
#TTj <- TTj[TTj$name!="NA",]

atm_res <- atm[atm$year.AD>1950,]
atm_res$year.AD <- as.numeric(atm_res$year.AD)
atm_res$year_plant.res <- atm_res$year.AD + plant_res

TT1 <- atm_res
TT1$TT <- years[1]
TT1$Delta14C_permil <- as.numeric(TT1$Delta14C_permil)
TT1$Fprimeatm <- TT1$Delta14C_permil/1000+1
lambda <- 1.21*10^-4
TT<-years[1]
k <- 1/TT
FCss <- k/(k+lambda)
Delta14C_ss <- ((FCss/(exp(-(1951-1950)/8267)))-1)*1000
TT1$FprimeC <- Delta14C_ss/1000 + 1
for(i in 2:length(TT1$Delta14C_permil)){
  TT1$FprimeC[i] <- k*TT1$Fprimeatm[i] + TT1$FprimeC[i-1] - k*TT1$FprimeC[i-1] - lambda*TT1$FprimeC[i-1]
}
TT1$Delta14C_res <- (TT1$FprimeC-1)*1000

Turnover <- list(TT1)
atm_res$Delta14C_permil <- as.numeric(atm_res$Delta14C_permil)

for(j in 2:length(years)){
  TT <- years[j]
  TTj <- atm_res
  TTj$TT <- TT
  TTj$Fprimeatm <- TTj$Delta14C_permil/1000+1
  k <- 1/TT
  FCss <- k/(k+lambda)
  Delta14C_ss <- ((FCss/(exp(-(2013-1950)/8267)))-1)*1000
  TTj$FprimeC <- Delta14C_ss/1000 + 1
  for(i in 2:length(TTj$Delta14C_permil)){
    TTj$FprimeC[i] <- k*TTj$Fprimeatm[i] + TTj$FprimeC[i-1] - k*TTj$FprimeC[i-1] - lambda*TTj$FprimeC[i-1]
TTj$Delta14C_res <- (TTj$FprimeC-1)*1000
  }
Turnover <- c(Turnover, list(TTj))
}
tail(data.frame(Turnover[1]))
```

3. Make a data frame with the turnover times and D14C values extracted from the data frames in the list
```{r}
for(j in 1:length(collyear)){
  year <- collyear[j]


  Delta14C <- numeric(length(Turnover))
  for(i in 1:length(Turnover)){
    Delta14C[i] <- data.frame(Turnover[i])[data.frame(Turnover[i])$year.AD==year,"Delta14C_res"]
  }
  Delta14C_plant.res <- numeric(length(Turnover))
  for(i in 1:length(Turnover)){
    Delta14C_plant.res[i] <- data.frame(Turnover[i])[data.frame(Turnover[i])$year_plant.res==year,"Delta14C_res"]
  }
  TT <- numeric(length(Turnover))
  for(i in 1:length(Turnover)){
    TT[i] <- data.frame(Turnover[i])[63,5]
  }
  assign(paste("TTwindows", year, sep="_"), data.frame(TT, Delta14C, Delta14C_plant.res))

}
```

Identify where each 14C data point falls on the appropriate windows dataframe.

Save whichever TTwindows data frames you want
```{r}
write.csv(TTwindows_2012, 'TTwindows/TTwindows_2012.csv', quote=FALSE, row.names=FALSE)
write.csv(TTwindows_2013, 'TTwindows/TTwindows_2013.csv', quote=FALSE, row.names=FALSE)
write.csv(TTwindows_2014, 'TTwindows/TTwindows_2014.csv', quote=FALSE, row.names=FALSE)


```